MSF_Groupwork-NBA_shotlog

### 2016-10-13 MSFGroupwork-NBAHotHand.Rmd
minor changes

# Find shooting percentage of each match

@@

game <- cast(data = df, GAME_ID1 + HOME_TEAM + AWAY_TEAM + LOCATION + player_name + W + FINAL_MARGIN~ FGM)

@@

game[, "FGA"] <- NA
for(i in 1:nrow(game)){
  game[i, "FGA"] <- game[i, "1"] + game[i, "0"]
}

@@

game[, "FG.percentage"] <- NA 
for (i in 1:nrow(game)){
  game[i, "FG.percentage"] <- round(((game[i, "1"]/game[i, "FGA"]) * 100), digits = 2)
}
```

# Impact of Super Star Players

@@

super.star.list <- c("lebron james", "james harden", "russell westbrook", "stephen curry", "anthony davis", "blake griffin", "klay thompson", "lamarcus aldridge") # players picked out
super.star <- game[game$player_name %in% super.star.list, c("player_name", "W", "LOCATION", "FINAL_MARGIN", "FGA", "FG.percentage")] # create a subset for these players

# Replace "W" and "L" with 1 and 0 respectively, 
super.star[, "W"] <- as.character(super.star[, "W"])
for (i in 1:nrow(super.star)) {
  if (super.star[i, "W"] == "W") super.star[i, "W"] <- 1
  if (super.star[i, "W"] == "L") super.star[i, "W"] <- 0
}
super.star[, "W"] <- as.numeric(super.star[, "W"])

ggplot(super.star) + geom_boxplot(aes(x = player_name, y = FGA, colour = W))
ggplot(super.star) + geom_boxplot(aes(x = player_name, y = FG.percentage, colour = W))
ggplot(super.star) + geom_point(aes(x = FINAL_MARGIN, y = FGA, colour = player_name))
ggplot(super.star) + geom_boxplot(aes(x = LOCATION, y = FINAL_MARGIN))

# t.test(super.star$FINAL_MARGIN[super.star$LOCATION == "H"], super.star$FINAL_MARGIN[super.star$LOCATION == "A"])

# Correlation test
cor.test(super.star$FINAL_MARGIN, super.star$FGA)
cor.test(super.star$FINAL_MARGIN, super.star$FG.percentage) # cor = 0.272

# Linear regression
summary(lm(FINAL_MARGIN ~ FGA + LOCATION, data = super.star)) # Final margin ~ FGA and location
summary(lm(FINAL_MARGIN ~ FG.percentage + LOCATION, data = super.star)) # Final margin ~ FG% and location
summary(lm(FINAL_MARGIN ~ FG.percentage + FGA + LOCATION, data= super.star))

summary(lm(FINAL_MARGIN ~ LOCATION, data = super.star)) # Final margin ~ FGA and location

>>>>

# Find field goal percentage (FG percentage) for each match

@@

shot.stats <- cast(data = df, GAME_ID1 + HOME_TEAM + AWAY_TEAM + LOCATION  + W + player_name + FINAL_MARGIN ~ FGM)

@@

shot.stats[, "FGA"] <- NA
for(i in 1:nrow(shot.stats)){
  shot.stats[i, "FGA"] <- shot.stats[i, "1"] + shot.stats[i, "0"]
}

@@

shot.stats[, "FG.percentage"] <- NA 
for (i in 1:nrow(shot.stats)){
  shot.stats[i, "FG.percentage"] <- round(((shot.stats[i, "1"]/shot.stats[i, "FGA"]) * 100), digits = 2)
}
```

# Impact of Top Scorers

@@

top.scorers.list <- c("paul millsap", "isaiah thomas", "brook lopez", "kemba walker", "jimmy butler", "mnta ellis", "ty lawson", "reggie jackson", "lebron james", "james harden", "russell westbrook", "stephen curry", "anthony davis", "blake griffin", "lamarcus aldridge", "cj miles", "kobe bryant", "marc gasol", "dwayne wade", "brandon knight", "andrew wiggins", "carmelo anthony", "nikola vucevic", "michael carter-williams", "eric bledsoe", "demarcus cousins", "kawhi leonard", "kyle lowry", "gordon hayward", "john wall") # players picked out
top.scorers <- shot.stats[shot.stats$player_name %in% top.scorers.list, c("player_name", "W", "LOCATION", "FINAL_MARGIN", "FGA", "FG.percentage")] # create a subset for these players

# Replace "W" and "L" with 1 and 0 respectively, 
top.scorers[, "W"] <- as.character(top.scorers[, "W"])
for (i in 1:nrow(top.scorers)) {
  if (top.scorers[i, "W"] == "W") top.scorers[i, "W"] <- 1
  if (top.scorers[i, "W"] == "L") top.scorers[i, "W"] <- 0
}
top.scorers[, "W"] <- as.numeric(top.scorers[, "W"])

ggplot(top.scorers) + geom_boxplot(aes(x = player_name, y = FGA, colour = W))
ggplot(top.scorers) + geom_boxplot(aes(x = player_name, y = FG.percentage, colour = W))
ggplot(top.scorers) + geom_point(aes(x = FINAL_MARGIN, y = FGA, colour = player_name))
ggplot(top.scorers) + geom_boxplot(aes(x = LOCATION, y = FINAL_MARGIN))

# t.test(top.scorers$FINAL_MARGIN[top.scorers$LOCATION == "H"], top.scorers$FINAL_MARGIN[top.scorers$LOCATION == "A"])

# Correlation test
cor.test(top.scorers$FINAL_MARGIN, top.scorers$FGA)
cor.test(top.scorers$FINAL_MARGIN, top.scorers$FG.percentage) # cor = 0.272

# Linear regression
summary(lm(FINAL_MARGIN ~ FGA + LOCATION, data = top.scorers)) # Final margin ~ FGA and location
summary(lm(FINAL_MARGIN ~ FG.percentage + LOCATION, data = top.scorers)) # Final margin ~ FG% and location
summary(lm(FINAL_MARGIN ~ FG.percentage + FGA + LOCATION, data= top.scorers))

summary(lm(FINAL_MARGIN ~ LOCATION, data = top.scorers)) # Final margin ~ FGA and location
